Model 

### 2020-04-27 05_estimation.Rmd
Remove inverse-distance matrix
The contiguous matrix should be sufficient

```{r tracts}
tracts_access <- read_rds("data/tracts_access.rds")
```

### Inverse distance weights
My Atlanta house price study considered that houses within 1.8 miles of each
other were "neighbors," with the strength of the relationship decaying with 
the inverse of the distance between them. We can build the same matrix using 
the population-weighted centroid of the tract as the observation point.

```{r Winv}
pop_weighted_centroids <- read_rds("data/pop_weighted_centroids.rds")

# determine which tracts are neighbors of each other. Need to be less than
# 1.8 miles away from the centroids
tracts.dnn <- dnearneigh(pop_weighted_centroids, 0, 1.8 * 5280)
# calculate the inverse distance to use as a weight on the neighbor connection
tract_dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))

tract_dists.inv <- lapply(tract_dists, function(x) 1 / x)
# get the spatial weights matrix and its trace to use in any impact analyses
Winv <- nb2listw(neighbours = tracts.dnn, glist = tract_dists.inv,
                 zero.policy = TRUE, style = "W")
print(Winv, zero.policy = TRUE)
```

@@

```{r Wcontig}
tracts.adj <- poly2nb(tracts_access)
Wcontig <- nb2listw(tracts.adj, style = "W", zero.policy = TRUE)
print(Wcontig, zero.policy = TRUE)
```

@@

```{r ols_vs_sem}
access_ols <- lm(update(base_formula, physact ~ . + access_ls), data = tracts_access)
access_sem_wd <- errorsarlm(update(base_formula, physact ~ . + access_ls),
                            data = tracts_access, listw = Winv, zero.policy = TRUE)
access_sem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
                            data = tracts_access, listw = Wcontig, zero.policy = TRUE)

ols_vs_sem <- list("OLS" = access_ols, "SEM dist" = access_sem_wd, 
                   "SEM cont" = access_sem_wd)
```

@@

sp_hausman(access_ols, access_sem_wd)
sp_hausman(access_ols, access_sem_wc)
```

@@

```{r access_slx}
access_slx_wd <- lmSLX(update(base_formula, physact ~ . + access_ls), 
                       data = tracts_access, listw = Winv, zero.policy = TRUE)
access_slx_wc <- lmSLX(update(base_formula, physact ~ . + access_ls), 
                       data = tracts_access, listw = Wcontig, zero.policy = TRUE)
access_sdem_wd <- errorsarlm(update(base_formula, physact ~ . + access_ls),
                            data = tracts_access, listw = Winv, zero.policy = TRUE,
                            Durbin = TRUE)
access_sdem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
                            data = tracts_access, listw = Wcontig, zero.policy = TRUE, 
                            Durbin = TRUE)
slx_vs_sdem <- list(
  "Dist SLX" = access_slx_wd, 
  "Dist SDEM" = access_sdem_wd, 
  "Contig SDEM" = access_sdem_wc,
  "Contig SLX" = access_slx_wc
)
```

As before, we can try a Hausman-style test, but in this case the covariance
matrix appears poorly defined and we therefore get a negative test statistic.
```{r slx_hausman}
slx_hausman <- function(slx, sdem) {
  b1 <- slx$coefficients
  b2 <- sdem$coefficients
  db <- b1 - b2

@@

  tibble(
    Hstat = t(db) %*% MASS::ginv(dV) %*% db, 
    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV), lower.tail = FALSE)
  )
}
slx_hausman(access_slx_wc, access_sdem_wc)
slx_hausman(access_slx_wd, access_sdem_wd)
```

@@

```{r lagged_vars}
contiglagged_vars <- tracts_access %>%
  st_set_geometry(NULL) %>%
  as_tibble() %>%
  transmute_at(
    vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other, physact),
    ~lag.listw(Wcontig, .)
  ) %>%
  mutate(geoid = tracts_access$geoid) %>%
  dplyr::select(geoid, everything())

names(contiglagged_vars)[-1] <- str_c("lag.", names(contiglagged_vars)[-1])
contiglagged_tracts <- tracts_access %>% left_join(contiglagged_vars, by = "geoid")
```

@@

```{r nolag_access}
access_slx_wc <- lm(update(
  base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
    lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls),
  data = contiglagged_tracts)

access_sdem_wc <- errorsarlm(update(
  base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
    lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls), 
  data = contiglagged_tracts, listw = Wcontig, zero.policy = TRUE)
```

@@

```{r estimate_sdems}
base_sdem <- update(access_sdem_wc, formula = . ~ . - access_ls,
                    data = contiglagged_tracts, listw = Wcontig, zero.policy = TRUE)

# estimate models
pa_access_sdm <- access_sdem_wc
pa_tweets_sdm  <- update(base_sdem, .~ . + tweets_ls)
pa_multi_sdm   <- update(base_sdem, .~ . + multi_ls)
pa_walk10_sdm  <- update(base_sdem, .~ . + walk_10)
```

@@

```{r access_sdm}
pa_models <- list("Base"        = base_sdem,
                  "Logsum"      = pa_access_sdm,
                  "Tweets"      = pa_tweets_sdm,
                  "Attributes"  = pa_multi_sdm,
                  "10-min walk" = pa_walk10_sdm)
```

>>>>

```{r bg_access}
bg_access <- read_rds("data/bg_access.rds")
```

The accessibility is calculated at the block group level, but the other information
(health, demographics) is available only at the tract level.

```{r tracts}
mydata <- bg_access %>% 
  dplyr::mutate(tract = substr(geoid, 0, 11)) %>%
  left_join(
    read_rds("data/tracts.rds") %>%
      st_set_geometry(NULL),
    by = c("tract" = "geoid")
  ) %>%
  filter(!is.na(households))
```

@@

```{r Wcontig}
areas_adj <- poly2nb(mydata)
Wcontig <- nb2listw(areas_adj, style = "W", zero.policy = TRUE)
print(Wcontig, zero.policy = TRUE)
```

@@

```{r ols_vs_sem}
access_ols <- lm(update(base_formula, physact ~ . + access_ls), data = mydata)
access_sem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
                            data = mydata, listw = Wcontig, zero.policy = TRUE)

ols_vs_sem <- list("OLS" = access_ols, "SEM" = access_sem_wc)
```

@@

sp_hausman(access_ols, access_sem_wc)
```

@@

```{r access_slx}
access_slx_wc <- lmSLX(update(base_formula, physact ~ . + access_ls), 
                       data = mydata, listw = Wcontig, zero.policy = TRUE)
access_sdem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
                            data = mydata, listw = Wcontig, zero.policy = TRUE, 
                            Durbin = TRUE)
slx_vs_sdem <- list(
  "SDEM" = access_sdem_wc,
  "SLX" = access_slx_wc
)
```

As before, we can try a Hausman-style test.
```{r slx_hausman}
slx_hausman <- function(slx, sdem) {
  b1 <- slx$coefficients
  b2 <- sdem$coefficients
  db <- b1 - b2

@@

  tibble(
    Hstat = t(db) %*% MASS::ginv(dV) %*% db, 
    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV), lower.tail = FALSE)
  )
}
slx_hausman(access_slx_wc, access_sdem_wc)
```

@@

```{r lagged_vars}
contiglagged_vars <- mydata %>%
  as_tibble() %>%
  transmute_at(
    vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other, physact),
    ~lag.listw(Wcontig, .)
  ) %>%
  mutate(geoid = mydata$geoid) %>%
  dplyr::select(geoid, everything())

names(contiglagged_vars)[-1] <- str_c("lag.", names(contiglagged_vars)[-1])
contiglagged_data <- mydata %>% left_join(contiglagged_vars, by = "geoid")
```

@@

```{r nolag_access}
access_slx_wc <- lm(update(
  base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
    lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls),
  data = contiglagged_data)

access_sdem_wc <- errorsarlm(update(
  base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
    lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls), 
  data = contiglagged_data, listw = Wcontig, zero.policy = TRUE)
```

@@

```{r estimate_sdems}
base_sdem <- update(access_sdem_wc, formula = . ~ . - access_ls,
                    data = contiglagged_data, listw = Wcontig, zero.policy = TRUE)

# estimate models
pa_access_sdm <- access_sdem_wc
pa_multi_sdm   <- update(base_sdem, .~ . + multi_ls)
```

@@

```{r access_sdm}
pa_models <- list("Base"        = base_sdem,
                  "Logsum"      = pa_access_sdm,
                  "Attributes"  = pa_multi_sdm)
```
